---
title: "Contextual Word Embeddings"
output:
  html_document: default
  html_notebook: default
---

```{r, message=FALSE, warning=FALSE}
library(dplyr)
library(tidytext)
library(wordVectors)
library(janeaustenr)
library(ggplot2)
library(Rtsne)
```

For an easy example I'll use the Austen books corpus in the ```janeaustenr``` package.

```{r}
original <- austen_books() %>%
  group_by(book) %>%
  mutate(line = row_number()) %>%
  ungroup()

original
```
#Preprocess
Now use tidytext magic to tokenize. Tidytext returns a tidy-format table, where each token is on its own row.

```{r}
tidy <- original %>%
  unnest_tokens(word, text)

tidy
```

Now let's make a tag for each book and prepend to a select set of words. For simplicity, let's go ahead and use the factor level. We'll use '#' as an arbitrary delimiter that we'll sacrifice later on because we aren't interested at all in how Austen's use of the pound sign changes between books. 
```{r}
tidy <- tidy %>%
  mutate(word = ifelse(word == "time", paste0(as.numeric(book), '#', word),word))
```
And now prepare for word vectorizing by collapsing all words, adding a space between tokens first, into a single character object and then writing to a txt file.
```{r}
tidy %>%
  select(word) %>%
  unlist() %>%
  paste(collapse = " ") %>%
  writeChar("words.txt")
```

#Vectorize
Run word2vec, passing in the txt file we just made.
```{r, message=FALSE, warning=FALSE}
vectors <- train_word2vec("words.txt")

```
We can check out the words most similar to "time" as used in Sense and Sensibility.
```{r}
nearest_to(vectors, vectors["1#time"])
```
compared with those most similar to "time" as used in Pride and Prejudice.
```{r}
nearest_to(vectors, vectors["2#time"])
```

#Visualize
We can get fancy and use t-SNE to visualize how they relate.
```{r}
vec <- vectors@.Data
plottable_vectors <- Rtsne(vec, dims = 2, theta = 0.8, perplexity = 30, verbose = TRUE)
```
Now we can plot on X&Y, coloring by book
```{r}
plot_df <- data_frame(x = plottable_vectors$Y[,1],
                      y = plottable_vectors$Y[,2],
                      labels = row.names(vec))

sp <- stringr::str_split_fixed(plot_df$labels, "#", 2)
plot_df <- cbind(plot_df, sp)
colnames(plot_df)[4] <- 'group'
colnames(plot_df)[5] <- 'excess'
plot_df <- plot_df %>%
  mutate(group = ifelse(excess=="", "none",as.character(group)))

ggplot(subset(plot_df, group != "none"), aes(x,y, color=group)) +
  geom_point() +
  ggtitle("Time in 6 different \nAusten Books")+
  theme_minimal()
```

Success!